{\sc Kalashnikov}: Fully Automatic Loop Free Program Synthesis by Bounded Model Checking

### 2013-10-04 paper/paper.tex
Started related work

\section{Related Work}
The most similar work to ours is {\sc brahma}~\cite{brahma}, which is also a method for
synthesizing loop-free bitvector programs.  Specifications for the

>>>>

\section{Related Work}
The most similar work to ours is {\sc brahma}~\cite{brahma}, which is also a method for
synthesizing loop-free bitvector programs.  In~\cite{brahma} the authors characterise
the program synthesis problem as a second order $\exists \forall$ formula, and
described the CEGIS algorithm for solving these formulae.  This algorithm reduces
the satisfiability of the $\exists \forall$ formula to the satisfiability of several
first order formulae, each of which can be decided using an off-the-shelf SMT solver.
{\sc Brahma} takes as input a specifcation (an SMT formula) and a library of components
(one component is more or less a single machine instruction).  It then finds
a permutation of the component library which satisfies the specification.  This
permutation is the final synthesised program.  In the event that the library does
not contain enough components to synthesise a correct program, the user is told
that the library is too small and is required to add more components until
the synthesis succeeds.  Each round of synthesis amounts to solving an
$\exists \forall$ formula that is quadratic in the size of the component library.

Our work represents an incremental improvement on {\sc brahma}.  We require the
user to supply a program specification written in C, but then ask nothing more of her.
Our encoding allows us to generate an $\exists \forall$ formula which is \emph{linear}
in the length of the shortest program satisfying the user's specification,
which we then check for satisfiability using the CEGIS algorithm.  It should
be noted that since the programs produced by {\sc brahma} are permutations of the
component library, the shortest correct program can be no longer than the size
of the library.

Another successful approach to program synthesis has been program sketching, in
particular the {\sc sketch} tool~\cite{sketch}.  With this method the user supplies
a program sketch, written in a C-like language, together with either a specification
(written in the same language) or a suite of unit tests.  The sketch is a skeleton
program which contains much of the high level structure of the final program,
but with several ``holes'' that {\sc sketch} fills in to meet the specification,
again using the CEGIS algorithm.

Program synthesis is strongly related to superoptimisation~\cite{superoptimisation},
which is the problem of taking a segment of code, usually written in C, and finding
a minimal program which has the same functionality.  The {\sc aha}~\cite{aha} tool
and the GNU superoptimiser~\cite{gnu-superoptimiser} both do superoptimisation of
C programs, both by enumerating possible programs and testing them on suitable inputs.
This search can be compiled down to native code using an optimising compiler,
so for short programs the method is extremely fast, however because of the exponential
blowup of the program space it is impractical for synthesising longer programs.
We incorporate this technique by using explicit state model checking in parallel
with symbolic model checking.
